Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-20 writeup/gz_hubble_data.tex
Sort individual FERENGI curves by f_z=0.3 and add more

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples.pdf}
\caption{Behavior of the normalized, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$. Measured vote fractions (red points) are fit with an exponential
function (Equation~\ref{eqn:fzeta}); the best-fit parameters are given above
each plot. Error bars are Poissonian, assuming a median of 40~votes per
galaxy.}
\label{fig:zeta_examples}
\end{figure*}

>>>>

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/zeta_examples_sorted.pdf}
\caption{Behavior of the normalized, weighted vote fractions of features
visible in a galaxy ($f_\textrm{features}$) as a function of redshift in the
artificial \ferengi{} images. Galaxies in this plot were randomly selected from
a distribution with $e=0$ and at least three detectable images in redshift bins
of $z\ge0.3$, and are sorted by \ffeaturesrest. Measured vote fractions (blue
solid line) are fit with an exponential function (red dashed line;
Equation~\ref{eqn:fzeta}); the best-fit parameter for $\zeta$ is given above
each plot.}
% Error bars are binomial for each f, symmetrised, then added in quadrature.
\label{fig:zeta_examples}
\end{figure*}
